% !TEX TS-program = XeLaTeX
Technological progress gives your \planet\ access to additional dice and other bonuses, increasing your options and allowing more powerful turns.  \tech\ is produced by \labs.  Each time one of your \labs\ is activated, you may check the leftmost box of your \tech\ track.
The track branches at certain points: once past these, you may check boxes in any branch you have started.  The upper branch of the \antimatter\ track reflects experimentation and advances in \antimatter\ for use in space travel.  The middle branch represents advances in \engineering.
\newline\newline
Various points on the track provide one-time or lasting benefits upon researching them (checking the indicated box).
\begin{itemize}
  \item \cure\ makes you immune to the \pandemic\ disaster.
  \item \antimatter\ (checking the first box of the upper shaded area) gives you access to the \bluedie\ for the rest of the game.
  \item \engineering\ research gives you access to the \blackdie\ for the rest of the game.
  \item \warpdrive\ gives you \reach\ (see next section) to all other players for the purposes of \military\ actions or \trade.
  \item \shields\ make your \squadrons\ (see \nameref{sec:military}, p.\pageref{sec:military}) more powerful for the purposes of defence.
  \item \lasers\ make your \squadrons\ (see \nameref{sec:military}, p.\pageref{sec:military}) more powerful for the purposes of attacking.
  \item Whenever you check a box with a \gainculture\ symbol as it's reward, you may cross any one box on the \culture\ grid.
  \item Whenever you check a box with a \gaincurrency\ symbol as it's reward, you may gain one \currency.
  \item Finishing any branch triggers the end of the game and provides a scoring bonus.
\end{itemize}
