% !TEX TS-program = XeLaTeX
The \planet\ is under constant threat from calamities and \pirate\ raids.  
\disasters\ are checked after the \diplomacy\ phase if any dice showing 1 still 
remain.  These dice are re-rolled and their new value will determine what 
disaster strikes.
\begin{enumerate}
  \item If players paid to re-roll any die during the \diplomacy\ there may be 
        no die to roll during this phase
  \item If any dice showing the value \texttt{1} \textit{do} remain at this 
        stage, they are rerolled separately from the rest.
  \item Each player looks at the results and checks the leftmost unchecked box 
        from the \disaster\ grid rows corresponding to those numbers.
  \item If any further \texttt{1}s resulted from the reroll, the process is then
        repeated until no \texttt{1}s remain.
  \item The rerolled dice are then placed with the rest and may be used normally
        during the ensuing \development\ phase.
\end{enumerate}
Whenever the third (shaded) box of any row of the \disaster\ grid is checked, 
the corresponding \disaster\ hits.  One row may only trigger once, so if those 
numbers are later rolled again, nothing happens.
\newline\newline
Many \disasters\ only trigger under certain conditions and/or offer the players
a choice.
\begin{itemize}
  \item \pandemic\ only affects players who have not yet researched \cure\ 
        (see \nameref{sec:disasters}, p.\pageref{sec:disasters}). The affected 
        player must cross over two \population\ or gain one \unhappiness.
  \item The damages of \war\ can be negated by \deploying\ one \squadron.  The 
        players who cannot or choose not to do this lose up to three \currency\ 
        and gain one \unhappiness.
  \item \terrorism\ affects players whose \unhappiness\ (in terms of crossed 
        boxes) is larger than their \happiness.  It can be prevented by 
        \deploying\ one \squadron\ and gaining one \unhappiness.  Otherwise, an 
        \armament\ (the player chooses which) is destroyed and cannot be used 
        for the rest of the game.  No new \armaments\ may be built in the same 
        space.  You may choose an opponent's \battleship\ as the target, but 
        they may prevent its destruction by deploying one \squadron.
\end{itemize}
Hardship breeds creativity: the triggering of some \disasters\ allows player to 
check any one box from the \culture\ grid.
