% !TEX TS-program = XeLaTeX
\asciiplanets\ is played in turns.  With the exception of the solo mode (see 
\nameref{sec:playercount}, p.\pageref{sec:playercount}), the number of turns is
not set beforehand.  Instead, the players take turns until one of several game 
end conditions (see \nameref{sec:endgame}, p.\pageref{sec:endgame}) is met.
\newline\newline
Each turn consists of five phases:
\begin{enumerate}
	\item \textbf{\dice}: The five dice are rolled.  Any player may do this (as 
        the results will be the same for all players)
	\item \textbf{\diplomacy}: The players discuss the results and may 
        collectively spend \currency\ to reroll some of the dice (see ]
        \nameref{sec:diplomacy}, p.\pageref{sec:diplomacy})
	\item \textbf{\disasters}: All dice still showing the value \texttt{1} are 
        rerolled.  This may result in \disasters\ being triggered (see 
        \nameref{sec:disasters}, p.\pageref{sec:disasters})
  \item \textbf{\development}: This is where most of the game action takes 
        place. The die faces are now considered final and the players take 
        actions simultaneously using the die results available to them.
  \item \textbf{\deployment}: Players may deploy \squadrons\ to perform one or 
        more \military\ actions (see \nameref{sec:military}, 
        p.\pageref{sec:military})
\end{enumerate}
The players then begin another turn if no game end conditions have been met.  
Otherwise, the scores will be calculated after the final \deployment\ phase and 
the player with the most points wins.
